% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009-2012 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

% GENERAL NOTE:  There may be some notes specific to myself.  If you're only interested in my LaTeX source or it doesn't make sense, please disregard it.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=black
    %urlcolor=mygreylink     % can put red here to better visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.40}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubsubheading}[2]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
        \textit{#1} & \textit{#2} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

%-----------------------------------------------------------
%General Resume Tips
%   No periods!  Technically, nothing in this document is a full sentence.
%   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
%   More tips on bottom of this LaTeX document.
%-----------------------------------------------------------

\begin{document}

\newcommand{\mywebheader}{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
    \textbf{\href{http://www.derekhildreth.com/}{\LARGE Kristian R. Kyvik}} & \href{mailto:kristianruizkyvik@gmail.com}{kristianruizkyvik@gmail.com}\\
    {\footnotesize \texttt{\colorbox{yellow}{[web version:  address \& phone omitted]}}} & \href{http://www.linkedin.com/in/kristianruizkyvik}{linkedin.com/in/kristianruizkyvik} \\
    \end{tabular*}
\\
\vspace{0.1in}}

% CHANGE HEADER SOURCE HERE
\mywebheader

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
    \begin{itemize}
        \item
            \ressubheading{\href{http://www.byui.edu}{Norwegian University of Sciences and Technology}}{Trondheim, Norway}{\href{http://www.byui.edu/csee/compe/default.htm}{Msc. Industrial Economics and Technology Management}; \href{http://www.ntnu.com/portfolio/unofficial_transcript.pdf}{GPA:4.06}}{Aug. 2012 -- Present}
                { \footnotesize
                \begin{itemize}
                    %\resitem{\textbf{Available for internship: July 23, 2009; Graduation follows internship}}
                    \resitem{Key Courses: Object Oriented Software Development, Data Structures, \href{http://derekhildreth.com/portfolio/Resume/catalog/class.asp1045.htm}{Computer Architecture}, \href{http://derekhildreth.com/portfolio/Resume/catalog/class.asp1073.htm}{Data Communications}, \href{http://derekhildreth.com/portfolio/Resume/catalog/class.asp1072.htm}{Real-Time and Embedded Systems}, \href{http://derekhildreth.com/portfolio/Resume/catalog/class.asp1069.htm}{Digital Systems Design}}
                    \resitem{\textbf{\href{http://www.byui.edu/Societies/Linux/}{ Voluntary Activities:}}}
                        \begin{itemize}
                            \resitem{ Member \& Buddy Program Coordinator at ESN (Erasmus Student Network)}
                            \resitem{ Member \& Main Organiser at BEST (Board of European Student of Technology)}
                            \resitem{ Workshop Contact and Performing Arts Functionary at ISFiT (International Student Festival in Trondheim)}
                        \end{itemize}
                \end{itemize}
                }
        \item
        \ressubheading{\href{http://www.byui.edu}{King's College London}}{London, United Kingdom}{\href{http://www.byui.edu/csee/compe/default.htm}{Exchange Year (during third year)}; \href{http://www.ntnu.com/portfolio/unofficial_transcript.pdf}}{Aug. 2014 -- Jun. 2015}
            { \footnotesize
            \begin{itemize}
                %\resitem{\textbf{Available for internship: July 23, 2009; Graduation follows internship}}
                \resitem{Key Courses: Object Oriented Software Development, Data Structures, \href{http://derekhildreth.com/portfolio/Resume/catalog/class.asp1045.htm}{Computer Architecture}, \href{http://derekhildreth.com/portfolio/Resume/catalog/class.asp1073.htm}{Data Communications}, \href{http://derekhildreth.com/portfolio/Resume/catalog/class.asp1072.htm}{Real-Time and Embedded Systems}, \href{http://derekhildreth.com/portfolio/Resume/catalog/class.asp1069.htm}{Digital Systems Design}}

            \end{itemize}
            }
        \item
        \ressubheading{\href{http://www.byui.edu}{IronHack}}{Barcelona, Spain}{\href{http://www.byui.edu/csee/compe/default.htm}{Intensive 8 week programming apprenticeship}; \href{http://www.ntnu.com/portfolio/unofficial_transcript.pdf}}{Jul. 2014 -- Aug. 2014}
            { \footnotesize
            \begin{itemize}
                %\resitem{\textbf{Available for internship: July 23, 2009; Graduation follows internship}}
                \resitem{Focused on TDD, pair-programming, self-teaching/troubleshooting}
                \resitem{Learned Front-end \& Back-end development, HTML5, CSS3, JavaScript, Git, Ruby, Rails, MVC, agile methods}
                \resitem{Final project became one of the finalists and was presented at the closing ceremony}¨
            \end{itemize}
            }

    \end{itemize} % End Education list

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Experience}
    \begin{itemize}
        \item
            \ressubheading{\href{http://www.embeddedarm.com}{TOAD London}}{London, United Kingdom}{Software Developer}{Nov. 2014 -- Aug. 2015}
                { \footnotesize
                \begin{itemize}
                    \resitem{Worked as a tourist guide for both Spanish and British groups (30-50 at a time).}
                \end{itemize}
                }
        \item
            \ressubheading{\href{http://www.oracle.com}{Norwegian University of Sciences and Technology}}{Trondheim, Norway}
                {Learning Assistant/ Facilitator at Experts in Team (EiT)}{Jan. 2014 -- Jun. 2014}
                { \footnotesize
                \begin{itemize}
                    \resitem{EiT is a course in which students apply their academic competence in interdisciplinary project.}
                    \resitem{I observed and provide feedback on the interaction of the team.}
                    \resitem{Planned activities to stimulate the team dynamics.}
                \end{itemize}
                }

            \ressubsubheading{Teaching Assistant in Dicrete Mathematics}{Aug. 2013 -- Feb. 2013}
                { \footnotesize
                \begin{itemize}
                    \resitem{Overlooked two weekly 2-hour tutorials in the subject TMA4140 Discrete Mathematics.}
                \end{itemize}
                }

        \item
            \ressubheading{\href{http://www.embeddedarm.com}{More \& Trondelag Guideservice AS}}{Trondheim, Norway}{Tourist Guide}{Jun. 2013 -- Aug. 2013}
                { \footnotesize
                \begin{itemize}
                    \resitem{Worked as a tourist guide for both Spanish and British groups (30-50 at a time).}
                \end{itemize}
                }

    \end{itemize}  % End Experience list

%%%%%%%%%%%%%%%%%%%%%%
\resheading{\href{http://www.derekhildreth.com/portfolio.php}{Skills}}
    \begin{description}
        \item[Technologies:] { \footnotesize Ruby, Python, Java, Javascript, MySQL, HTML, CSS, Rails, Angular, Bootstrap, Git, Regex, JSON}

        \item[Languages:] { \footnotesize
            Spanish (Fluent), English (Fluent), Norwegian (Advanced), Catalan (Fluent), French (Intermidiate)
        }

    \end{description} % End Skills list

\resheading{\href{http://www.derekhildreth.com/portfolio.php}{Projects}}

\begin{description}
\item[HackShow Finalist:] { \footnotesize Made it to the top 5 projects of the cohort with Quizzapp, an online platform for creating, playing and sharing music quizzes.}

\item[Prize to the Best Use of Twilio API:] { \footnotesize Created a native android mobile application that could retrieve directions to any location that worked without data or internet connection. We used the Twilio API, a backend server powered with Flask, and the Google Maps API.}

\item[elWorldtrip:] { \footnotesize This was a project that involved traveling around the world with my whole family for an entire year. The six of us (my parents and my three sisters) crossed more than 30 countries in 5 diverents continents in our old Toyota Land Cruiser. It was a trip to explore the world, learn about foreign cultures (as well as ourselves) and, last but not least, to spread consciousness about Diabetis (my father has been a diabetic for more than 50 years). http://elworldtrip.com/}

\end{description}

\end{document}


%%%%%%%%%%%%%%%%%%%%%%
% Would have completed this if I had not had all projects listed under "Skills".
% Still a good idea.  See if I can fit it in somewhere...  Otherwise, just print it out and bring it to an interview if needed.
%%%%%%%%%%%%%%%%%%%%%%
\newpage
\myheader
\resheading{Hardware Engineering Projects} % If printed as a seperate page, get more detailed in the descriptions!  What type of processor?  What program used? Etc.

    \begin{description}
        \item[4 and 8 bit RISC CPUs] {\footnotesize Simple CPUs designed using CircuitMaker (no HDL) which contained ALUs, counters, registers, and 1K RAM all designed from scratch}
        \item[Simple Calculator] {\footnotesize Designed a simple calculator from the ground up using Xilinx ISE and Verilog HDL} % Get schematic block diagram for this one!
        \item[Stereo Amplifier] {\footnotesize Contained I/O as well as bass, treble, and volume controls}
        \item[Power Supply Basics] {\footnotesize Learned about the very basics of power supply design using transformers, rectifiers, and zener diodes and voltage regulators.}
        \item[Parallel Port Game Controller] {\footnotesize Went through the start to finish development process of a game controller including driver development, microprocessor  \& ADC design (8255 MicroBoard; N.I.    ADC0809), and PCB design}
        \item[Portable Microphone Amplifier] {\footnotesize Utilized a series of transistors to amplify sound in a room with a potentiometer as volume control}
        \item[MP3 Player] {\footnotesize Developed an MP3 player using the Analog Devices BlackFin BF533 microprocessor and EZ-KIT development kit which utilized interrupts and audio codec}  % get link to block diagram for this one!
        \item[INL Remote Cell Phone Control] {\footnotesize Senior project which developed a prototype for Idaho National Laboratories allowing them to remote control a cell phone via 802.11g and bluetooth at a range greater than 6000ft consisting of 3 major components: central control, wireless medium, and embedded systems for chuckar box}
        \item[Inverted Pendulum] {\footnotesize Used sliding mode feedback control and inverted pendulum kit to keep metal rod standing vertially on a swingin arm}
        \item[FM Transmitter] {\footnotesize Built a simple FM Transmitter based off of given schematics as an introduction to FM modulation signals}
    \end{description}


\resheading{Software Engineering Projects}  % There really are a TON of projects I can put on this, but here are some major ones:
    \begin{description}
        \item[Book Keyword Scanner] {\footnotesize Developed a program which will take any input file and, given a keyword search, will return the frequency of that word }
        \item[Pedigree Chart] {\footnotesize Developed a program which will parse through a pedigree file and display a pedigree chart in the command line}
        \item[Factory Nail Rejection] {\footnotesize This program was simulating a factory which produced nails that had to be a very specific length, and if it wasn't, the program would reject it}
        \item[Calendar Program] {\footnotesize Given the time and date to display, the calendar program would display a simple calendar on the command line which took into account leap years}
        \item[Normal Distribution] {\footnotesize This program simulated the classic wheel of fortune blinko game where several thousand chip were statistially recorded and displayed as they dropped into a board filled with pegs}
        \item[RSA Encryption] {\footnotesize Developed an application which utilized the RSA encryption method to encrypt and decrypt messages}
    \end{description}

\end{document}

%Only Print References If Requested!  Maybe even put it in it's own page.  Must have same heading as first page.
%%%%%%%%%%%%%%%%%%%%%%
\newpage
\myheader
\resheading{References}
    \begin{center}
        \begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}  l l l }
            Toby Rummans & Eric Karl & Gordon Smith \\
            Entry Level Web Developer & Computer Science \& Engineering  & Technology Support Specialist \\
            \vspace{10pt}
            Memolinkcorp & BYU-Idaho & BYU-Idaho \\
            [removed] & 525 South Center St. & 525 South Center St.  \\
            Denver, CO 80210 & Rexburg ID 83460 & Rexburg ID 83460 \\
            [removed] & (208) 496-3097 & (208) 496-2816 \\
        \end{tabular*}
    \end{center}

% \end{document}


% ADDITIONAL WORK EXPERIENCE NOT INCLUDED   OR OLD

        \item
            \ressubheading{\href{http://www.rexburgmotorsports.com/}{Rexburg Motorsports}}{Rexburg, ID}{Computer Systems Administrator}{Aug. 2006 -- Oct. 2006}
                { \footnotesize
                \begin{itemize}
                            \resitem{Managed file and application servers running Windows 2003 Server}
                            \resitem{Performed all levels of hardware and software systems support for 40 computers and 10 printers}
                \end{itemize}
                }

        \item
            \ressubheading{Bresnan Communications}{Billings, MT}{Teir 1 Technical Support}{Jan. 2006 -- April 2006}
                { \footnotesize
                \begin{itemize}
                    \resitem{Provided Bresnan customers with technical support over the phone.}
                    \resitem{Receieved training on resolving networking, cable TV, and VOIP issues.}
                \end{itemize}
                }

        \item
            \ressubheading{Northwestern Energy}{Billings, MT}{Summer Gas/Electrical Engineer}{May 2004 -- April 2005}
                \begin{itemize}
                    \resitem{Interned with full time Gas/Electrical Engineers.}
                    \resitem{Documented, mapped, and marked city streetlights using MS Access, GTViewer, FRAMME, and CAD.}
                \end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%
% GENERAL RESUME NOTES %
%%%%%%%%%%%%%%%%%%%%%%%%
Need to brush up on the skills section?  Here are some really good ideas:

- Communication: The ability to express and interpret ideas and convey knowledge.
Skills like speaking effectively, writing concisely, listening attentively, expressing ideas,
reporting information, editing, interviewing, and facilitating group discussion.

- Research and Planning: The ability to search for specific knowledge and formulate a
program for a definite course of action. Skills like forecasting, predicting, identifying
issues, finding alternatives, gathering information, solving problems, setting goals,
extracting information, and developing strategies.

- Human Relations: The ability to apply interpersonal skills to resolve conflict, relate to
people, and help people. Skills like providing support for others, listening, delegating
with respect, representing others, asserting, developing rapport, and perceiving
feelings.

- Management, Organization, Leadership: The ability to supervise others and guide
individuals and groups towards the completion of tasks. Skills like managing groups,
selling ideas, making decisions, managing conflict, coordinating tasks, teaching,
enlisting help.

Source:
http://www.squawkfox.com/2009/03/08/6-action-words-that-make-your-resume-rock/

Other Resources:
http://www.tvmier.com/Resume_Education.html

